---
title: "Querying the information on blocks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Querying the information on blocks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

A detailed description of how blocks are produced on the TRON blockchain can be found in the official documentation. At a high level, blocks are logical units that combine transactions that took place on the blockchain within a certain period of time. On the TRON network this time is set to 3 seconds.

There are two main functions in the `tronr` package to make block-specific queries. The first one, `get_block_info()`, retrieves a set of attributes either for the latest generated block or for a specific block referred to by its number. In both cases, this function will return a [nested tibble](https://tidyr.tidyverse.org/articles/nest.html "Nested data in R") - see help file (`?get_block_info`) for definitions of the respective columns.

```{r get-block-info, message=FALSE}
library(tronr)
library(dplyr)
library(tidyr)

# Get data for the latest block (argument `latest = TRUE`):
r1 <- get_block_info(latest = TRUE)
glimpse(r1)

# Get data for a specific block:
r2 <- get_block_info(latest = FALSE, block_number = "26810333")
glimpse(r2)
```

One of the most important columns in the returned tibble is `tx` - a list with one element, which contains a tibble with some basic info on transactions associated with the queried block:

```{r block-tx-info}
r1$tx[[1]] %>% glimpse()
```

Another function, `get_blocks_for_time_range()`, retrieves attributes of the blocks produced within a user-specified period of time. This period is definied with the `min_timestamp` and `max_timestamp` arguments, both of which expect Unix timestamps (including milliseconds):

```{r blocks-for-time-range, message=FALSE}
# Use utility function `to_unix_timestamp` to convert POSIXct
# datetime values to Unix timestamps
r <- get_blocks_for_time_range(
  min_timestamp = "1551715200000",
  max_timestamp = "1551715210000"
)

glimpse(r)
```

In contrast to the `get_block_info()` function, `get_blocks_for_time_range()` does not return data on transactions associated with the respective blocks - this is to speed up the query and processing time, which can be substantial for longer periods of time. However, if transaction data are required, users can apply `get_block_info()` to the list of blocks returned by `get_blocks_for_time_range()`:

```{r get-tx-for-list-of-blocks, message=FALSE}
r_tx <- sapply(r$block_number, 
               function(x) {get_block_info(latest = FALSE,
                                          block_number = x)
               }, simplify = FALSE) %>% 
  bind_rows()

# Overview of the resultant nested tibble:
glimpse(r_tx)

# Unnest data on transactions:
r_tx %>% 
  select(block_number, tx) %>% 
  unnest(cols = tx) %>% 
  glimpse()
```

\
