---
title: "Smart contract events"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Querying the smart contract events}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

When a smart contract is run, the underlying TRON Virtual Machine ([TVM](https://developers.tron.network/docs/vm-introduction)) emits various bits of information in the form of logs, which are known as *events*. Events often contain useful data related to how the respective smart contract operates. The `tronr` package offers several functions that can be used to query events based on the block number, transaction ID, or contract address.

Events associated with the latest block can be retrieved using the `get_events_of_latest_block()` function, which returns a [nested tibble](https://tidyr.tidyverse.org/articles/nest.html "Nested data in R"):

```{r events-in-latest-block, message=FALSE}
library(tronr)
library(dplyr)
library(tidyr)

latest_events <- get_events_of_latest_block()
glimpse(latest_events)
```

Event data are stored in the list-column `event_data`, where each element is a named list with attributes of the respective event, e.g.:

```{r event-data}
latest_events$event_data[[1]]

latest_events$event_data[[2]]
```

The above examples illustrate that elements of the `event_data` column are contract- and event-specific. As the structure of event data emitted by every smart contract existing on the TRON blockchain is impossible to know *a priori*, these event attributes are returned "as-is", i.e. without any parsing or other pre-processing. Users are advised to develop their own, task-specific, logic to process event attributes.

Event data associated with a specific block can be retrieved using the function `get_events_by_block_number()`:

```{r events-by-block, message=FALSE}
block_event <- get_events_by_block_number(block_number = "15354550")

glimpse(block_event)
```

Similarly, functions `get_events_by_tx_id()` and `get_events_by_contact_address()` allow one to retrieve event data for a specific transaction or smart contract address:

```{r other-event-functions, message=FALSE}
# Query by transaction ID:
tx_id <- "270e992bf22a271008032ec09a51616ed963b74f4d808b0fd74fc82341a81391"
tx_events <- get_events_by_tx_id(tx_id = tx_id)
glimpse(tx_events)

# Query by contract address (bound to a time range):
contract_address <- "TKttnV3FSY1iEoAwB4N52WK2DxdV94KpSd"
min_timestamp <- "1576317786000"
max_timestamp <- "1576317996000"

contr_events <- get_events_by_contract_address(
  address = contract_address,
  min_timestamp = min_timestamp,
  max_timestamp = max_timestamp
)
glimpse(contr_events)

# Еhe last query could also be filtered by the name
# of a specifc event of interest:
contr_events_filtered <- get_events_by_contract_address(
  address = contract_address,
  min_timestamp = min_timestamp,
  max_timestamp = max_timestamp,
  event_name = "Transfer",
  direction = "asc"
)
glimpse(contr_events_filtered)
```
