---
title: "Querying the balance of a TRON account"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Querying the balance of a TRON account}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

There are two functions in `tronr` that can be used to query the *current* balance of a TRON account. Note that the term "account" here refers to both wallet-like accounts *and* smart contracts.

The `get_account_trx_balance()` function retrieves the current amount of Tronix (TRX) held by an account. The main argument of this function is `address`, which (similar to all `tronr` functions that take `address` as one of their inputs) accepts account addresses in either [`base58check`](https://bitcoin.stackexchange.com/questions/75527/eli5-what-is-base58check-encoding) (start with `T`) or `hex` format (start with `41`).

```{r trx-balance, message=FALSE}
library(tronr)
library(dplyr)
library(tidyr)

(bal <- get_account_trx_balance(address = "TQjaZ9FD473QBTdUzMLmSyoGB6Yz1CGpux"))
```

The obtained TRX balance can be converted to a fiat currency, such as USD, using the `get_current_trx_price()` function (this function makes a call to the CoinGecko API to obtain the current TRX price in the respective currency):

```{r trx-price}
price <- get_current_trx_price(vs_currencies = c("usd"))

bal$trx_balance * price$trx_price
```

A more comprehensive view of an account's balance can be obtained using the `get_account_balance()` function, which returns a [nested tibble](https://tidyr.tidyverse.org/articles/nest.html "An overview of nested data"):

```{r get-account-balance}

r <- get_account_balance(address = "TQjaZ9FD473QBTdUzMLmSyoGB6Yz1CGpux")

glimpse(r)
```

The nested structure of this tibble can be seen in columns `bandwidth` (account's current [energy and bandwidth resources](https://tronprotocol.github.io/documentation-en/introduction/overview/#8-resource-model "TRON resources model")), `trc20` ([TRC-20 tokens](https://developers.tron.network/docs/trc20 "TRC-20 tokens") held by the account), and `trc10` ([TRC-10 tokens](https://developers.tron.network/docs/trc10 "TRC-10 tokens") held by the account). Each of these columns contains a list with a single element - another tibble with the corresponding data. These nested data can be retrieved either by using the standard R indexing or by applying the [`tidyr::unnest()`](https://tidyr.tidyverse.org/reference/nest.html "Unnesting the nested tibbles") function:

```{r get-nested-data-by-indexing}
# Retrieve data on the TRC-20 tokens held by the account,
# using the standard R indexing:
r$trc20[[1]]

# Retrieve the same data by unnesting the tibble:
r %>% select(trc20) %>% unnest(cols = trc20)
```
